Environment modeling in \tool

### 2022-05-02 paper.tex
pass section 4 and 5

This section shows the evaluation benchmarks of running Coreutils programs on \tool with both two file systems and KLEE. \tool has two file system implementations, one written in the source language level (directly porting KLEE's POSIX filesystem), one written in the target language level as runtime library. We also run the same program on KLEE to compare the performance with \tool. Because we directly reuse KLEE's file system as the source level implementation, comparison between \tool with KLEE's POSIX file system and KLEE is fair and can measure the efficiency of this two symbolic execution engines. We will use \tool/POSIX to represent our framework with KLEE's filesystem implementation, \tool/FS to represent our framework with the internal target language level file system implementation and KLEE/POSIX to represent KLEE with its file system. We choose echo from Coreutils programs for testing and we perform all the experiment on the Intel(R) Xeon(R) Platinum 8168 CPU @ 2.70GHz 192 core cpu on server bigdata2.cs.purdue.edu. We use g++ with -O3 to compile the generated C++ code as mentioned in section \ref{coreutilstests}. The running time is shown in Table \ref{tab:coreutils_benchmarks_echo} and Figure \ref{fig:speedup}.\par

@@

\caption{Comparing the running times of \tool/POSIX, \tool/FS and KLEE/POSIX

@@

  \hline
                & \textbf{\#Sym}    & 6     & 7     & 8    & 9     & 10      \\
                & \textbf{\#Path}   & 575     & 1679    & 4971  & 14825  & 44362      \\
                 \hline
  \textbf{KLEE/POSIX} &\textbf{Time(s)} & 4.52  & 12.17  & 38.20 & 147.54  & 438.99   \\
  \textbf{\tool/POSIX}& \textbf{Time(s)}  & 0.78 & 2.28 & 7.32 & 23.25 & 76.08 \\
  \textbf{\tool/FS}   &\textbf{Time(s)}  & 0.55 & 1.59 & 5.07 & 16.60  & 54.84  \\
                 \hline
  \textbf{\tool/POSIX over}   &  \\
  \textbf{KLEE/POSIX}   &\textbf{Speedup}  & 5.79 & 5.34 & 5.22 & 6.35  & 5.77  \\
  \hline
  \textbf{\tool/FS over}   &  \\
  \textbf{\tool/POSIX}   &\textbf{Speedup}  & 1.42 & 1.43 & 1.44 & 1.40  & 1.39  \\
  \hline
  \end{tabular}
\label{tab:coreutils_benchmarks_echo}
\vspace{-1em}
\end{table}
\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.6]{evaluationplot.pdf}
  \caption{Running time of KLEE/POSIX, \tool/POSIX and \tool/FS}
  \label{fig:speedup}
\end{figure}
We first observe that KLEE/POSIX, \tool/POSIX and \tool/FS explore the same number of paths, this validate the correctness of our symbolic execution engine and our internal file system using KLEE as a reference. \par
The result demonstrates that our internal file system has faithfully modeled KLEE's POSIX file system. We can observe that our internal file system also performs better than KLEE's POSIX file system in our engine with a steady 1.4x speedup based on the comparison between \tool/FS and \tool/POSIX. This validate our observation in Section \ref{twofsimpl} that although implementing file system in the source language level has the benefit of flexibility and portability, it lacks performance and efficiency as the file system always executes on the control and memory abstraction of the underlying engine. Levels of indirection will cause a significant performance degrading.\par
Besides the comparison between the two file system implementations in \tool, the comparison between \tool/POSIX and KLEE/POSIX demonstrates that our framework really out performs KLEE. \tool achieves a 5x to 6x speedup over KLEE while analyzing the same program and obtaining the same path coverage. This speedup comes from two aspects, the eliminated interpretation overhead, and the optimization opportunity enabled by code generation. This proves our claim that we could realize efficient symbolic execution by adopting modern compilation and code generation techniques.
\section{Conclusion}\label{conclusion}
We discuss two different approaches of modeling environment in the context of symbolic execution compiler. Modern code generation techniques allow implementing the file system environment both at source language level an the target language level. The former approach is flexible and portable while the later approach has the advantage of performance and efficiency. We test Coreutils program as a benchmark for environment modeling in symbolic execution. We overcome several obstacles towards testing Coreutils and optimized the compilation time. The final Coreutils benchmark of both file system implementations in \tool and KLEE validates our claim and deepen our understanding of symbolic execution.
\bibliographystyle{acm}
\bibliography{paper}
\end{document}
\endinput

>>>>

This section shows the evaluation benchmarks of running Coreutils programs on \tool with two file systems and KLEE. \tool has two file system implementations, one written at the source language level (directly reusing KLEE's POSIX filesystem) and one written at the target language level as runtime library. We also run the same program on KLEE to compare the performance with \tool. Because we directly reuse KLEE's file system as the source level implementation, comparisons between \tool with KLEE's POSIX file system and KLEE is fair and can measure the efficiency of these two symbolic execution engines. We will use \tool/POSIX to represent our framework with KLEE's filesystem implementation, \tool/FS to represent our framework with the internal file system implementation, and KLEE/POSIX to represent KLEE with its file system. We choose echo from Coreutils programs for testing, and we perform all the experiments on the Intel(R) Xeon(R) Platinum 8168 CPU @ 2.70GHz 192 core CPU on server bigdata2.cs.purdue.edu. We use g++ with -O3 to compile the generated C++ code as mentioned in section \ref{coreutilstests}. The running time is shown in Table \ref{tab:coreutils_benchmarks_echo} and Figure \ref{fig:speedup}.\par

@@

\caption{Comparing the running time of \tool/POSIX, \tool/FS and KLEE/POSIX

@@

  \hline
                & \textbf{\#Sym}    & 6     & 7     & 8    & 9     & 10      \\
                & \textbf{\#Path}   & 575     & 1679    & 4971  & 14825  & 44362      \\
                 \hline
  \textbf{KLEE/POSIX} &\textbf{Time(s)} & 4.52  & 12.17  & 38.20 & 147.54  & 438.99   \\
  \textbf{\tool/POSIX}& \textbf{Time(s)}  & 0.78 & 2.28 & 7.32 & 23.25 & 76.08 \\
  \textbf{\tool/FS}   &\textbf{Time(s)}  & 0.55 & 1.59 & 5.07 & 16.60  & 54.84  \\
                 \hline
  \textbf{\tool/POSIX over}   &  \\
  \textbf{KLEE/POSIX}   &\textbf{Speedup}  & 5.79 & 5.34 & 5.22 & 6.35  & 5.77  \\
  \hline
  \textbf{\tool/FS over}   &  \\
  \textbf{\tool/POSIX}   &\textbf{Speedup}  & 1.42 & 1.43 & 1.44 & 1.40  & 1.39  \\
  \hline
  \end{tabular}
\label{tab:coreutils_benchmarks_echo}
\vspace{-1em}
\end{table}
\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.6]{evaluationplot.pdf}
  \caption{Running time of KLEE/POSIX, \tool/POSIX and \tool/FS}
  \label{fig:speedup}
\end{figure}
We first observe that KLEE/POSIX, \tool/POSIX, and \tool/FS explore the same number of paths. This validates the correctness of our symbolic execution engine and our internal file system using KLEE as a reference. \par
The result demonstrates that our internal file system has faithfully modeled KLEE's POSIX file system. Our internal file system also performs better than KLEE's POSIX file system in our engine with a steady 1.4x speedup based on the comparison between \tool/FS and \tool/POSIX. This result validates our observation in Section \ref{twofsimpl} that although implementing file system at the source language level has the benefit of flexibility and portability, it lacks performance and efficiency as the file system always executes on the control and memory abstraction of the underlying engine. Levels of indirection will cause significant performance degradation.\par
The comparison between \tool/POSIX and KLEE/POSIX demonstrates that our framework significantly outperforms KLEE. \tool achieves a 5x to 6x speedup over KLEE while analyzing the same program and obtaining the same path coverage. This speedup comes from the eliminated interpretation overhead and the optimization opportunity enabled by code generation. This proves our claim that we could realize efficient symbolic execution by adopting modern compilation and code generation techniques.
\section{Conclusion}\label{conclusion}
In this paper, we discuss two different approaches to modeling environment in the context of symbolic execution compiler. Modern code generation techniques allow implementing the file system environment at the source and target language levels. The former approach is flexible and portable, while the latter has better performance and efficiency. We optimize the overall compilation time after targetting Coreutils as the environment modeling test suite. The final Coreutils benchmark of both file system implementations in \tool and KLEE validates our claim and deepens our understanding of symbolic execution.
\bibliographystyle{acm}
\bibliography{paper}
\end{document}
\endinput
